{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-06-30 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
before meeting

\section{Background and Related Work}
In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them.
While government agencies define various sets of boundaries to partition the geographical space into  
However, the spatial extent of these defined unit

Although, their physical boundaries can be adjacent or distant, based on various connections amongst themselves, such as social-economic relations and commute patterns of citizens, certain groups of urban regions are more strongly connected as clusters than others.

@@

\subsection{Potential limitation of }
To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
However, the low-resolution mobility data collected from census records~\citep{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\citep{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\citep{gonzalez2008understanding}.
In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008understanding}. However, the data is often limited in spatial scale (e.g. within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2010geolife} and~\citep{rhee2011levy} respectively. Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g. taxi), which may only be accessible for a certain group of people~\citep{kung2014exploring}.

@@

In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns. Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries. It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\citep{cranshaw2012livehoods, hasan2013understanding}.
In addition, it presents some unique advantages that make it suitable for studying human mobility patterns.
For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka2014geo}, which is almost impossible for other mobility datasets.
More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).

@@

>>>>

\section{Background and Related Work}
In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them.
For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into units at different spatial scale, for instances, states, counties or census tracts and electoral districts.
\cite{
However, the spatial extent of these defined units overlaps via connections of various human activities amongst themselves, such as social-economic relations and commute patterns of citizens, where certain groups of units are more strongly connected as clusters than others.

@@

\subsection{Large-scale mobility network from geo-located Twitter data}
To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
However, the low-resolution mobility data collected from census records~\citep{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\citep{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\citep{gonzalez2008understanding}.
In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008understanding}. However, the data is often limited in spatial scale (e.g. within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2010geolife} and~\citep{rhee2011levy} respectively. Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g. taxi), which may only be accessible for a certain group of people~\citep{kung2014exploring}.

@@

In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns. Twitter is one of the most popular platforms and is been actively used in many countries. It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data.
It presents some unique advantages that make it suitable for studying human mobility patterns.
For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka2014geo}, which is almost impossible for other mobility datasets.
More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).

@@

\bibitem[\protect\citeauthoryear{Blanford {\itshape{et~al.}}}{2015}]{blanford2015}
Blanford, J.I., Huang, Z., Savelyev, A. and MacEachren, A.M., 2015. Geo-located tweets. enhancing mobility maps and capturing cross-border movement. PloS one, 10(6), p.e0129202.
